Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Paper
Fixed Typo

## Idealized Methodology

@@

### Budget Allocation

-

## Idealized Survey

@@

If you have any inquiries or need assistance with this survye, please contact us at:

>>>>

# Idealized Methodology

@@

## Budget Allocation

- Sampling and Data Collection (Advertisements and Recruitment Platforms): $40,000
- Participant Incentives (Prize Pool): $20,000
- Survey Design and Testing: $20,000
- Data Analysis and Validation: $20,000

# Idealized Survey

@@

If you have any inquiries or need assistance with this survey, please contact us at:
